---
params:
  data: "./Datasets/Opics.dat"
  date_from: "2020-03-18"
  
title: "Operations Metrics"
author: "Rajiv Gangadharan"
date: "18/08/2020"
output: 
  flexdashboard::flex_dashboard:
      orientation: columns
      vertical_layout: fill
      social: ["twitter","facebook","menu"]

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(flexdashboard) # libraries for controlling current rendering
source("./Common/jirametrics.R")
options(dplyr.summarise.inform = FALSE)
fileName <- params$data
date_from <- params$date_from
#fileName <- "./Datasets/Opics.dat"
#date_from <- "2020-03-18"

df <- readDataset(fileName)
tib <- df %>% 
      as_tibble() %>%
      mutate(crdt = toDate(Created),
             updt = toDate(Updated),
             cldt = toDate(Closed),
             cylt = as.numeric(getAge(crdt, cldt))
      ) %>%
      filter(cldt >= as.Date(date_from))
```


Throughput {.storyboard}
===========================================

### **Completed items/Week** Tells us the number of work items (stories) completed aggregated for each week which is an indication of how stable the throughput is.

```{r completed_items_week, include=TRUE, echo=FALSE}

stories <- tib %>% filter(Type == "Story")

stories_grouped_by_week <- stories %>% 
      mutate(WeekBegining = lubridate::floor_date(cldt, unit="weeks", week_start = 1)) %>%
      mutate(Week = lubridate::isoweek(cldt)) %>% group_by(Week)

stories_ncount_by_week <- stories_grouped_by_week %>% ungroup() %>% 
                          group_by(WeekBegining) %>% summarise(WeeklyCount = n())
ggplotly(ggplot(stories_ncount_by_week, aes(x=WeekBegining, y=WeeklyCount)) +
  geom_line(color=finastra_colors["charcoal"]) + 
    geom_point(color=finastra_colors["crimson"]) +
    xlab("Week") + ylab("Count of work items") + 
  scale_fill_manual(values=branded_pal()(1)) + finastra_theme)

```


### **Throughput (Count/Date)** tells us the number of stories delivered aggregated every week. The date is the begining monday of every week.

```{r stories_wk_agg, include=TRUE, echo=FALSE}


stories_wk_agg <- stories %>% 
                  mutate(FloorDate = lubridate::floor_date(cldt, unit="weeks", week_start = 1)) %>%
                  mutate(Week = lubridate::isoweek(cldt)) %>%
                  group_by(FloorDate, Priority)  %>% 
                  summarise(nclosed = n()) 


plot_stories_wk_agg <- ggplot(stories_wk_agg, aes(x=FloorDate, y=nclosed, fill=Priority)) +
    geom_bar(stat="identity") +
    xlab("Reporting Period") +
    ylab("Throughput") +
    scale_x_date(date_labels = "%b/%y", date_breaks = "2 weeks") +
    scale_fill_manual(values=branded_pal()(4)) +
    finastra_theme +
    theme(axis.text.x = element_text(angle = 90))

ggplotly(plot_stories_wk_agg)

```

### **Throughput (#Weeks/Count)** Tells us; How many weeks do we have were the throughput has a particular number? Is this the sustainable pace of delivery?


```{r stories_ncount_agg, include=TRUE, echo=FALSE}



stories_nweek_with_ncount <- stories_grouped_by_week %>% 
      summarise(ncount = n()) %>% ungroup() %>% 
      group_by(ncount) %>% summarise(nweeks=n())

ggplotly(ggplot(stories_nweek_with_ncount, aes(x=ncount, y=nweeks)) +
    geom_bar(stat="identity") +
    ylab("# Weeks with this throughput") +
    xlab("Throughput Value (#Stories in one calender week)") +
    scale_fill_manual(values=branded_pal()(1)) +
    finastra_theme)
```


